Critical Temperature of YBCO and BSCCO Superconductors

### 2014-12-12 Draft.tex
cleaned up sections
Data, analysis, concl, and abstract fixed up as good as I think it can
get.

\textcolor{blue}{don't leave us guessing what your results are! An abstract should ``stand-alone'' containing the key information needed to know what was done, how it was done, and what your key results were. Your result wasn't that you discovered superconductivity, or that you measured the critical temperature. Your result is that you found it to be a particular value, and it either agreed or disagreed with previous reports in the literature, that it indicated your material was either single phase or multiple phase (if you saw multiple transitions) and that you were able confirm the phase(s) or not from the transition temperature(s).}

Superconductors are materials that lose their electrical resistance  when they fall below a certain temperature. This is called the critical temperature. We determine the critical temperatures to be $xx \pm yy \text{ K}$ and $xx \pm yy \text{ K}$ for $\text{Yt}\text{Ba}_{2}\text{Cu}_{3}\text{O}_{7-\delta}$.
We find a single phase transition at $110\pm vv \text{ K}$ for $\text{Bi}_{2}\text{Sr}_{2}\text{Ca}_{n-1}\text{Cu}_{n}\text{O}_{2n+4}$.
The critical temperatures are found by passing a fixed current through the superconducting sample and measuring the change in voltage across the sample to determine its resistance. 
We give the critical temperature as the temperature halfway through the transition from non-zero resistance to zero resistance. Previous measurement of the critical temperature for YBCO give a critical temperature of 91 K. Our critical temperature for BSCCO is in agreement with previous measurements for $n=3$ phase found in the literature.    
This confirms that our BSCCO consists of mainly $n=3$ as it was stated it the manual that came with our samples.

@@

\begin{figure}[h!]
\centering
\includegraphics[width=7in]{thermocouple_voltage_vs_temp.png}
\caption{Figure 1: \textcolor{blue}{PROOFREAD!} Plot of Temperature and thermocouple voltage transcribed from the Colorado Superconductor Inc experiment manual, with fit lines across different sections.}
\label{TCplot}
\end{figure}

We gathered data across two warm-ups of the YBCO sample, the first at equal time intervals between points (see Fig. \ref{YBCOplot1}) and the second focusing on taking more points during the transition period than elsewhere (see Fig. \ref{YBCOplot2}).

In order to determine the critical temperature, we found the point along the transition period that was \textcolor{red}{exactly in between}\textcolor{blue}{do you mean halfway between?} the trend line for resistance during non-superconductivity and the trend line for resistance during superconductivity, and noted the corresponding temperature. The error in our voltage readings was very low (on the order of 0.000005mV), so the larger element of error is looking at the width of the transition zone, which was defined between the first points to clearly deviate from the trend lines. This yielded results of a $T_C$ of 98.03K and 98.67K per trial, with a range of 91K to 100K and 94K to 101K, respectively.

\textcolor{red}{does this mean your first transition occurs at }$T_C = 98.0 \pm 4.5 \text{ K}$ \textcolor{red}{ or that the transition begins at 91 K, ends at 100 K, and has a midpoint at 98 K? If the latter, what do you take to be the uncertainty in your determination of that midpoint? Also, you mention two trials, but only show one. Finally, why 4 sig figs for the critical temperature, if your uncertainty is on the order of 0.5 to 4.5 K, depending on how you define it. } 
\textcolor{blue}{That said, I like the method used to find the 1/2 way point (by drawing a line with 1/2 the slope seen in the resistive state). If you don't yet have a criteria for uncertainty for that value, one common definition is from 10 percent to 90 percent. So you could plot lines with slopes that are 10 percent and 90 percent to find those boundry points.}

@@

\textcolor{red}{where is your data on critical currents? You measured the transition for other current values as well. You should show the data, and then either extrapolate the current dependence to the zero current limit, or show your data doesn't show a current dependence for your range of values. There are two parameters of interest in regard to current dependence, by the way. One would be the critical temperature. The other would be the width of the transition (from zero to ``normal'' resistive state)}.

Next we looked at a sample of BSCCO gathered through the two-phase lock-in amplifier. Only one trial was performed, though data was gathered every 3 seconds for 3 hours. Once the data was plotted, the same procedure was used as with the YBCO sample to determine the critical temperature (see Fig. \ref{BSCCOplot1}). The critical temperature $T_C$ here was 110K, with a range of 101K to 119K. Of particular interest was the trend during the early pre-superconducting period. While certainly not truly ceasing to superconduct, there appeared to be some jumps in resistance during the superconductive phase, shown closely in Fig. \ref{BSCCOplot2}. On closer inspection, while there is clearly some upward trend and movement not seen in the YBCO sample, it is not clear enough to pinpoint any specific jumps.

@@

Superconductivity was clearly achieved in both the YBCO and the BSCCO samples, and their transition to being non-superconductive as their temperature increased was recorded. Graphical analysis yielded a critical temperature for YBCO of \textcolor{red}{fix this:} 98.35K $pm$ 7K and for BSCCO of 110K $pm$ 9K. According to the \textcolor{red}{Teachspin} manual, YBCO has a critical temperature of 92K, which is within our margin of error; similarly, the BSCCO sample was noted as having a critical temperature of 105K, again within our margin of error. The strange behavior seen during the end of the superconducting phase of the BSCCO sample may also have had to do with the fact that BSCCO can have two other critical temperatures. The general formula is $\text{Bi}_{2,1}\text{Sr}_{n+1}\text{Ca}_{\text{n}-1}\text{Cu}_{\text{n}}\text{O}_{2n+4+\delta}$. While the sample we had was specified for $n=3$, it is quite possible that other variations were present in our sample, each with their own critical temperature: $T_C$ for $n=1$ is 80K and $T_C$ for $n=2$ is 90K. \textcolor{blue}{what is your source for this information about Tc values for n  = 1, 2, and 3?} While we did not get as cold as 80K, we could be seeing some sections stop superconducting around 90K, alongside the already non-superconducting $n=1$ material, giving us a not truly flat superconducting zone.

\textcolor{red}{citations should include the ``teachspin'' manual (or the manual you really used) in addition to the 3 listed below. }

>>>>

Superconductors are materials that lose their electrical resistance when they fall below a certain temperature, called the critical temperature. We determined the critical temperatures for $\text{Yt}\text{Ba}_{2}\text{Cu}_{3}\text{O}_{7-\delta}$ to be $98.35\textrm{ K} \pm 7\textrm{ K}$. We found a single phase transition at $110\text{ K}\pm 9 \text{ K}$ for $\text{Bi}_{2}\text{Sr}_{2}\text{Ca}_{n-1}\text{Cu}_{n}\text{O}_{2n+4}$ as well.
The critical temperatures are found by passing a fixed current through a superconducting sample and measuring the change in voltage across the sample to determine its resistance. We describe the critical temperature as the temperature halfway through the transition from non-zero resistance to zero resistance. Previous measurement of the critical temperature for YBCO gives a critical temperature of 91 K. Our critical temperature for BSCCO is in agreement with previous measurements for $n=3$ phase found in the literature. This confirms that our BSCCO consists of mainly $n=3$, as indicated in the manual that came with our samples. We also saw agreement with a gneral decrease in critical temperature with an increase in current run through the YBCO sample, however the transition was uneven and distorted, so a specific difference in critical temperature could not be determined.

@@

\begin{figure}[h!]
\centering
\includegraphics[width=7in]{thermocouple_voltage_vs_temp.png}
\caption{Plot of temperature vs thermocouple voltage transcribed from the Colorado Superconductor Inc experiment manual, with fit lines across different sections.}
\label{TCplot}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=7in]{i250_ma_plot_of_resistor_voltage_vs_temperature.png}
\caption{Plot of resistor voltage vs temperature for a current of 250mA, with rebound effect representative of trials with currents above 1mA.}
\label{ReboundPlot}
\end{figure}

To find a reasonable starting current, we ran warm up trials with currents of 250mA, 100mA, 50mA, and 1mA on the YBCO sample. For all voltages above 1mA, when analyzed the resistor voltage vs temperature graphs displayed a bizarre rebound effect where there would be an increase in resistance before a sudden and severe drop, then followed by an increase into non-superconductivity (see Fig \ref{ReboundPlot}). As a result, we took our main data using 1mA current. We gathered data at 1mA across two warm-ups of the YBCO sample, the first at equal time intervals between points (see Fig. \ref{YBCOplot1}) and the second focusing on taking more points during the transition period than elsewhere (see Fig. \ref{YBCOplot2}).

In order to determine the critical temperature, we located the point along the transition period curve that was halfway between the trend line for resistance during non-superconductivity and the trend line for resistance during superconductivity, and noted the corresponding temperature. The error in our voltage readings was very low (on the order of 0.000005mV). The larger error contribution is related to the width of the transition zone. Defining the positive error as the temperature point where the resistance is at 90\% of the non-superconducting edge, and the negative error as the temperature point where the resistance is at 10\% of the non-superconducting edge, we obtained a range of  91K to 100K and 94K to 101K, for each trial respectively. This yields a final result of $T_{C}=98.03\textrm{K}\pm7\textrm{K}$ and $T_{C}=98.67\textrm{K}\pm4.67\textrm{K}$, respectively (using the greater of the positive and negative error to be conservative).

@@

\begin{figure}[h!]
\centering
\includegraphics[width=7in]{100ma_current_ybco_critical_temperature}
\caption{Plot of resistor voltage vs temperature for a current of 100mA during transition from superconducting to non-superconducting.}
\label{100mA}
\end{figure}

Despite troubles with rebound at higher currents, a video of the transition from superconducting to non-superconducting at a current of 100mA was obtained, and is shown in Fig \ref{100mA}. While the shaped following the rebound is distorted, and it is hard to identify a single point as the critical temperature – given the double curve effect – the 1mA YBCO trial is superconducting above 90K while the 100mA the sample has already begun the transition and has left pure superconducting by 90K.

Next we looked at a sample of BSCCO gathered through the two-phase lock-in amplifier. Only one trial was performed, though data was gathered every 3 seconds for 3 hours. Once the data was plotted, the same procedure was used as with the YBCO sample to determine the critical temperature (see Fig. \ref{BSCCOplot1}). The critical temperature $T_C$ here was 110K, with a range of 101K to 119K (10\% to 90\%) for an error of $\pm$ 9K. Of particular interest was the trend during the early pre-superconducting period. While certainly not truly ceasing to superconduct, there appeared to be some jumps in resistance during the superconductive phase, shown closely in Fig. \ref{BSCCOplot2}. On closer inspection, while there is clearly some upward trend and movement not seen in the YBCO sample, it is not clear enough to pinpoint any specific jumps.

@@

Superconductivity was clearly achieved in both the YBCO and the BSCCO samples, and their transition to being non-superconductive as their temperature increased was recorded. Graphical analysis yielded a critical temperature for YBCO of 98.35K $\pm$ 7K and for BSCCO of 110K $pm$ 9K. According to the Colorado Superconductor Inc manual, YBCO has a critical temperature of 92K, which is within our margin of error; similarly, the BSCCO sample was noted as having a critical temperature of 105K, again within our margin of error. The strange behavior seen during the end of the superconducting phase of the BSCCO sample may also have had to do with the fact that BSCCO can have two other critical temperatures. The general formula is $\text{Bi}_{2,1}\text{Sr}_{n+1}\text{Ca}_{\text{n}-1}\text{Cu}_{\text{n}}\text{O}_{2n+4+\delta}$. While the sample we had was specified for $n=3$, it is quite possible that other variations were present in our sample, each with their own critical temperature: $T_C$ for $n=1$ is 80K and $T_C$ for $n=2$ is 90K. \cite{colo} While we did not get as cold as 80K, we could be seeing some sections stop superconducting around 90K, alongside the already non-superconducting $n=1$ material, giving us a not truly flat superconducting zone. Finally, looking at the transition for YBCO with a current of 100mA, despite problems identifying a strict number for the critical temperature, the transition to non-superconducting clearly happens at a lower temperature then for 1mA. This is consistent with expectations since more energy from the increased current means that less thermal energy from warming up is needed to impart enough energy to stop the superconducting state within the YBCO crystals.
